comgen-outline

### 2017-09-02 paper/comgen-paper.Rmd
begin replacing prevalence w feature-probability

abstract: > 
    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Birds fly").
    The language of generalizations is ubiquitous in everyday discourse and child-directed speech. 
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    The major issue in formalizing *genericity* is in determining what which such statements are true or false.
    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Birds fly"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind"). 
    Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
    The results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

@@

These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of category having a property) is only incidentally related to generic meaning. 
**Conceptual accounts** of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012]. 
From this perspective, the statement "Bishops move diagonally" is true not because most bishops move diagonally, but rather because those are the rules of chess.
With this perspective, @Leslie2007 proposes that generics express a cognitively primitive, default generalization. 
The *generics as default* view argues that certain principles explain how generics become true or false.
"Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know if you are to survive in a hostile world.
This theory correctly predicted that generics that convey striking properties would be true even if the property was relatively uncommon [e.g., "Sharks attack swimmers"; @Cimpian2010; @Prasada2013].
"Robins lay eggs" can be thought of as conveying a *characteristic property*, which permits its felicity despite only 50\% having the feature [@Prasada2006; @Prasada2013].

@@

Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
The properties can vary greatly (e.g., having fur, causing jitters, typing). 
Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **prevalence**: 
$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
We denote prevalence as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency.
]

@@

If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability. 
One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
For generalizations, the threshold would apply to the subjective probability or *prevalence* $h$:

@@

Following standard treatment from formal semantics, we represent the semantic content of an utterance by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ for prevalence values $h$ greater than threshold $\theta$, and $0$ otherwise. 
Logical quantifiers can be described using such a semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?

@@

Given the semantic likelihood function defined in Eq. \ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over the prevalence $P(h)$:

@@

Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the prevalence $h$ according to the meaning of an utterance $u$.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
$P(h)$ represents the listener's prior world knowledge concerning the relevant prevalences $h$.
The particular form of the **prevalence prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.

@@

In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Birds lay eggs" is good; "Birds are female" is not) based on some known or believed prevalence $h$ (e.g., only female birds lay eggs).
Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe a **speaker model** as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq. \ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific value of prevalence $h$ that he is trying to communicate.
Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the prevalence of the property in the category. 
In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution:
$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
]

@@

The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate $h$ to the listener $L$, in comparison to alternative utterances.
We specify a single alternative utterance corresponding to *not saying the generalization*:
With just these two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments or sentence *endorsement* [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

@@

The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability that utterance vs. silence accurate conveys to a naive listener a prevalence $h$ in a referent-category (e.g., the \% of robins that lay eggs).
This probability is given by $L(h \mid u, \theta)$ (Eq. \ref{eq:S1}) and depends upon  the listener's *a priori* beliefs about the prevalence $h$ in question: $P(h)$ (Eq. \ref{eq:L0}), as well as the referent-category prevalence $h$ (Eq. \ref{eq:S1}).
Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
For purposes of illustration, we present different hypothetical priors on prevalence $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).

@@

```{r simulations, fig.cap = "Prior distributions over the prevalence of a feature (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions. The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 9, fig.height=5}
all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
  mutate(Distribution = factor(Distribution, levels = 
                             c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
                                labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")),
         PriorShape = factor(PriorShape, levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
                             labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         ) %>%
  ggplot(., aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = Distribution, fill = Distribution))+
    geom_density(#stat= 'identity', 
                aes(y = ..scaled..),
                 size = 0.6, alpha = 0.7, adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    #scale_color_solarized()+
    #scale_fill_solarized()+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence h") +
    ylab("Scaled probability density") +
  facet_grid(PriorShape~Distribution, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0))
```

These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
The fixed-threshold model rules out only the lowest possible prevalence ($h \sim 0$) and returns a posterior very similar to the prior.
The behavior of the generalization is distinct from a fixed-threshold model: The higher the prevalence $h$, the more likely it is after hearing the generalization.^[
The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
If the threshold $\theta$ is very high, only the highest prevalences $h$ would pass the threshold.
If the threshold $\theta$ is slightly lower but still high, the highest prevalences $h$ would still pass the threshold, as would some that are slightly lower.
As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
]

Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high prevalence values; this prior could be over the prevalence of the feature *barks* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
]
The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.

How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
In each case, we must consider the prevalence prior for the feature:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
"Robins lay eggs", however, has a lot of informational content.

@@

In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
For these simulations, we had specify the prevalence prior $P(h)$.
In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.

@@

Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
That is, "Mosquitos carry malaria" and "Birds lay eggs" are reasonable things to say, but "Birds are female" is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
We validate these simulations empirically by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} and the prevalence of the category that the speaker model seeks to convey (the *referent-category* prevalence) $h$ in Eq. \ref{eq:S1} (Expt. 1a).

<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g. "Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g. "Lions lay eggs.").
In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.

To compare the model to empirical truth judgments, we measure the prior distribution over prevalence of these properties (Expt. 1a).
We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
In particular, we hypothesize that different kind--property relations [e.g., *principled* v. *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the prevalence prior. 
If, in fact, the prevalence prior is a manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

After having validated a measure of the prevalence prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt. 1b).
In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model. 
To preview our results, we find that only our formulation of an uncertain threshold RSA model is able to account for the flexibility in generic endorsement.

@@

## Experiment 1a: Measuring the Prevalence Prior for Categories

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
].

>>>>

abstract: > 
    Generalizations are central to human understanding and language provides simple ways to convey generalizations (e.g., "Dogs bark").
    The language of generalizations is ubiquitous in everyday discourse and child-directed speech. 
    Yet the meaning of these expressions is philosophically puzzling (e.g., not all birds fly) and has resisted precise formalization.
    The major issue in formalizing *genericity* is in determining what which such statements are true or false.
    Using a probabilistic model of pragmatic reasoning, we explore the hypothesis that the meaning of such linguistic expressions is *simple but underspecified*, and that general communicative principles can be used to establish a more precise meaning in context. 
    To test this theory, we examine endorsements of generalizations about three different domains: generalizations about categories (*generic language* e.g., "Dogs bark"), events (*habitual language* e.g., "John runs"), and causes (*causal language* e.g., "Staring at the sun makes you go blind"). 
    Across these diverse domains, we find that our model explains human endorsements of generalizations in language, while simpler models do not.
    This is the first formal theory that makes precise, quantitative predictions about human understanding of generalizations in language.
    The results suggest that central phenomena of genericity emerge from the interaction of diverse prior beliefs about properties with general communicative principles.

@@

These observations have led to proposals that the statistics of the feature (e.g., the prevalence or probability of a member of category having a property) is only incidentally related to generic meaning. 
*Conceptual accounts* of generics emphasize the structure of *generic knowledge* [@Prasada2000], and view generic utterances as the way of expressing special, mental relationships between kinds and properties [@Leslie2008; @Prasada2012]. 
From this perspective, the statement "Bishops move diagonally" is true not because most bishops move diagonally, but rather because those are the rules of chess.
With this perspective, @Leslie2007 proposes that generics express a cognitively primitive, default generalization. 
The *generics as default* view argues that certain principles explain how generics become true or false.
"Mosquitos carry malaria" conveys a dangerous or *striking property*, which is useful to know if you are to survive in a hostile world.
This theory correctly predicted that generics that convey striking properties would be true even if the property was relatively uncommon [e.g., "Sharks attack swimmers"; @Cimpian2010; @Prasada2013].
"Robins lay eggs" can be thought of as conveying a *characteristic property*, which permits its felicity despite only 50\% having the feature [@Prasada2006; @Prasada2013].

@@

Generalizations are used to make predictions about properties of instances that an agent has yet to experience [@HumeTHN].
People readily predict that a new dog will have fur, drinking a new cup of coffee will cause jitters, and a new day will find me typing.
In each case, we assign a specific exemplar $x$ to a category $k$, and make a prediction that it will have property $f$. 
The entities can be objects (a dog), events (a coffee drink), or more fine grained types (me on a given day).
The properties can vary greatly (e.g., having fur, causing jitters, typing). 
Yet the prediction for a new entity can be described as a *predictive probability*, which we will denote throughout the paper as $h$ and refer to as the **feature-probability**: 
$h = P(x \in f \mid x \in k)$, the probability that $x$ will have $f$ given that it is in $k$.^[
We denote feature-probability as $h$ to emphasize that it is a latent *hypothesis*, and not necessarily an observable frequency or prevalence.
]

@@

If generalization from observations can be described using probability, then it seems  natural to consider the semantic content of an utterance that conveys generalization also to be relating to probability. 
One very simple semantic theory is a *threshold semantics*: an utterance is true is some quantity or *degree* is above a threshold.
For generalizations, the threshold would apply to the *feature-probability* $h$:

@@

Following standard treatment from formal semantics, we represent the semantic content of an utterance by the Kronecker delta function  $\delta_{\denote{u}(h, \theta)}$, which here returns probabilities proportional to $1$ for feature-probabilities $h$ greater than threshold $\theta$, and $0$ otherwise. 
Logical quantifiers can be described using such a semantics (i.e., *some* is $h > 0$, all is $h = 1$).
What threshold $\theta$ should be used for the generic generalization?

@@

Given the semantic likelihood function defined in Eq. \ref{eq:delta} and the prior distribution over thresholds $\theta$, we can formalize a **listener model** by specifying a prior distribution over feature-probabilities $P(h)$:

@@

Equation \ref{eq:L0} is a model of a Bayesian listener $L$ who updates her beliefs about the feature-probability $h$ according to the meaning of an utterance $u$.
$\delta_{\denote{u}(h, \theta)}$ is the likelihood term in Bayes' Rule and represents the literal semantic content of an utterance.
$P(h)$ represents the listener's prior world knowledge concerning the relevant feature-probabilities $h$.
The particular form of the **feature-probability prior** $P(h)$ plausibly depends upon the kind of property or event in question and could be structured as a result of deeper conceptual knowledge about properties and events [@Griffiths2005; @Tenenbaum2006; @Kemp2008].
This component of the model provides a potential bridge to conceptual accounts of generics [e.g., @Leslie2007; @Prasada2006; @Prasada2013].
Contrary to these accounts, in our model, conceptual structure is represented in listeners' knowledge of the world $P(h)$ and not in the semantic content of the utterance $u_{gen}$.

@@

In this paper, we are interested in explaining the variable *endorsements* of generalizations (e.g., "Robins lay eggs" is good; "Robins are female" is not) based on some known or believed feature-probability $h$ in a referent category (e.g., only female robins lay eggs).
Following the Rational Speech Act (RSA) framework [@Goodman2016], we describe a **speaker model** as a Bayesian decision of whether or not to say the generalization to the listener $L$ (Eq. \ref{eq:L0}).^[A more general version of this model can relax the assumption that the speaker has access to a specific feature-probability $h$ that he is trying to communicate.
Rather, the speaker may have a belief distribution over $h$ for the category $k$, corresponding to the speaker's beliefs about the feature-probability of the property in the category. 
In this situation, we would define the speaker's utility to be the expected value of the informativity, which integrates over her belief distribution:
$S(u \mid k) \propto \exp{(\lambda \cdot {\mathbb E}_{h\sim P_{k}} \ln{ \int_{\theta} L(h, \theta \mid u)} \diff \theta )}$
]

@@

The speaker's decision to say an utterance (e.g., the generalization) is determined by how well it would communicate the **referent feature-probability** $h$ to the listener $L$, in comparison to alternative utterances.
We specify a single alternative utterance corresponding to *not saying the generalization*:
With just these two alternatives (say the generalization vs. not), the model can be interpreted as a model of felicity judgments or sentence *endorsement* [@Degen2014]. 
Formally, we consider the negative alternative as the option of staying quiet, which carries no information content^[
This alternative can be realized in at least two other ways: the speaker could have said the negation of the utterance (i.e., *The generalization is not true.*) or the negative generalization (i.e., *The opposite is true.*, e.g., *Ks do not have F*).
All results reported are similar for these two alternatives, and we use the alternative of the *silent* utterance for simplicity.
]:

@@

The RSA model defined in the previous section predicts that the endorsement of a generalization depends upon the probability that utterance vs. silence accurate conveys to a naive listener a feature-probability $h$ in a referent-category (e.g., the \% of robins that lay eggs).
This probability of successful communication is given by $L(h \mid u, \theta)$ (Eq. \ref{eq:S1}) and depends upon the listener's *a priori* beliefs about the feature-probability in question: $P(h)$ (Eq. \ref{eq:L0}), as well as the referent-category feature-probability $h$ (Eq. \ref{eq:S1}).
Predictions for endorsement depend upon how well the listener's posterior on $h$  upon hearing a generalization matches an $h$ that the speaker wants to convey in comparison to how well the listener's prior matches (which would result from the speaker staying silent).
For purposes of illustration, we present different hypothetical priors on feature-probabilities $P(h)$, together with listener $L$ posterior distributions on $h$ after hearing utterances corresponding to (i) the underspecified threshold semantics as well as (ii) a comparison model where the threshold is fixed near-0, corresponding intuitively to the quantifier *some* (Figure \ref{fig:simulations}).

@@

```{r simulations, fig.cap = "Prior distributions over feature-probabilities (Left; grey) and listener model posterior distributions upon hearing an utterance with an uncertain threshold (Middle; red) and a fixed threshold (Right; blue), for five different schematic prior distributions. The uncertain threshold (Middle; red) is hypothesized to correspond to utterances that convey generalizations, while the fixed threshold (Right; blue) is a control model. Shapes of the priors were chosen to intuitivly correspond to properties labeling the distributions.", fig.width = 9, fig.height=5}
all.simulations %>%
  mutate(Distribution = paste(Distribution, utterance, sep = "_")) %>%
  filter(Distribution != "Some", Distribution != "Most", Distribution != "Prior_generic") %>%
  mutate(Distribution = factor(Distribution, levels = 
                             c("Prior_some",  "Posterior_Generalization_generic", "Posterior_Generalization_some"),
                                labels = c("Prior/Silence",  "Generalization (Uncertain threshold)", "Fixed threshold")),
         PriorShape = factor(PriorShape, levels = c("uniform", "barks","laysEggs","carriesMalaria","isFemale"),
                             labels = c("uniform", "bark","lay eggs","carry malaria","are female")
                                  #"eatsFood","areSick", "uniformRare", 
                                  #"carriesMalaria"
                                  )
         ) %>%
  ggplot(., aes(x = value, #y = prob, 
                #lty = Distribution, 
                color = Distribution, fill = Distribution))+
    geom_density(#stat= 'identity', 
                aes(y = ..scaled..),
                 size = 0.6, alpha = 0.7, adjust = 1.5)+
    #geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
    theme_few() +
    #scale_color_solarized()+
    #scale_fill_solarized()+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
   scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 0.5, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Feature-probability h") +
    ylab("Scaled probability density") +
  facet_grid(PriorShape~Distribution, scales = 'free')+
  guides(fill = F, color = F)+
  theme(strip.text.y = element_text(angle = 0))
```

These different semantic models make different predictions easily seen when considering a uniform prior distribution over $h$ (Figure\ \@ref(fig:simulations); top row).
The fixed-threshold model rules out only the lowest possible feature-probabilities ($h \sim 0$) and returns a posterior very similar to the prior.
The behavior of the generalization is distinct from a fixed-threshold model: The higher the feature-probability $h$, the more likely it is after hearing the generalization.^[
The intuition behind the model's behavior can be gleaned by imagining what the listener model $L$ would believe given different thresholds, and averaging over those possibilities.
If the threshold $\theta$ is very high, only the highest feature-probability $h$ would pass the threshold.
If the threshold $\theta$ is slightly lower but still high, the highest feature-probabilitys $h$ would still pass the threshold, as would some that are slightly lower.
As the threshold $\theta$ takes on lower and lower values, more and more $h$'s would surpass it.
When $\theta$ is very low, almost all $h$ are consistent with it (akin to fixed-threshold model).
The listener averages over these possibilities: $h$'s with higher values pass more thresholds and the result is that higher $h$'s are more likely *a posteriori*.
]

Next, we consider a few classic cases from the literature on generics to demonstrate the kind of inferences our listener model would draw from different generic statements.
The strength of a listener's inference about $h$ (i.e., how prevalent is the feature?) depends in systematic ways on the prior belief distribution over $h$.
In Figure\ \@ref(fig:simulations) (row 2), we show a schematic prior distribution that is bimodal with peaks near 0\% and some high feature-probability values; this prior could be over the feature-probability of *barking* because many kinds of creatures do not bark (i.e., have $h \sim 0$; e.g., cats), but *for those that do have members that bark*, many of them bark (i.e., have some high $h$).
The fixed threshold model (right column) struggles to differentiate those that generally do not have the feature from those that usually have the feature, returning a posterior distribution very similar to the prior.^[
We model "those that do not generally have the feature" as a Beta distribution with an expected value (mean) close to zero. 
The fact that this component of the prior is not just a Delta function at 0\% reflects the intuitive possibility that some members of a kind who do not generally have the feature (e.g., a cat who barks) could somehow acquire the feature from accidental or transient causes (e.g., a strange genetic mutation).
]
The uncertain threshold model, however, easily rules out the categories that do not generally have the feature and strongly signals the property is widespread in the category.

How does the model handle the puzzling case of "Robins lay eggs" vs. "Robins are female"?
In each case, we must consider the feature-probability prior:  $P(h_\text{lay eggs})$ and $P(h_\text{are female})$.
For being female, no matter what animal category a person might think of, the feature is prevalent in the exact same proprotion (i.e., 50\% of X are female; Figure\ \@ref(fig:simulations) bottom row).
For laying eggs, it really depends: If a person thinks of a falcon, then 50\% of that category lays eggs; if a person thinks of a bear, then 0\% of them lay eggs.
This dependency is reflected in the corresponding $P(h)$, which is a bimodal distribution with peaks near-0\% and near-50\% (Figure\ \@ref(fig:simulations) row 3).
For both priors, the interpretation upon hearing the generalization is the same (i.e., roughly 50\% of the category has the feature; Figure\ \@ref(fig:simulations) rows and 5, middle red panel).
The difference in endorsement comes from the comparison to the prior: For being female, the listener is very likely to arrive at 50\% under her prior, but for laying egges, this is not the case. 
In other words, "Robins are female" has little very informational content as the listener's posterior is nearly identical with her prior (i.e., it doesn't matter if the speaker says the generalization or stays silent).
"Robins lay eggs", however, has a lot of informational content.

@@

In sum, these simulations show that the behavior of the uncertain-threshold semantics is distinct from both the prior distribution over probability $h$, as well as the inferences derived from a fixed-threshold semantics.
For these simulations, we had specify the feature-probability priors $P(h)$.
In the rest of this paper, we both meausure and manipulate $P(h)$ and examine the behavior of the speaker model in three case studies: generalizations about categories, events, and causes.

@@

Any theory of generic language must explain its puzzling flexibility of usage with respect to feature-probability.
That is, "Mosquitos carry malaria" and "Robins lay eggs" are reasonable things to say, but "Robins are female" is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section.
We validate these simulations empirically by measuring the prior belief distribution over the feature-probabilities $P(h)$ used in Eq. \ref{eq:L0} and the referent-category feature-probability that the speaker model seeks to convey (the *referent feature-probability*) $h$ in Eq. \ref{eq:S1} (Expt. 1a).

<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: *characteristic* (e.g., "Ducks have wings."), *minority* (e.g., "Robins lay eggs."), *striking* (e.g. "Mosquitos carry malaria."), *false generalization* (e.g., "Robins are female."), and *absent features* (e.g. "Lions lay eggs.").
In additional to the canonical cases from the linguistics literature, we select sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low, medium, and high feature-probability properties.

To compare the model to empirical truth judgments, we measure the prior distribution over feature-probabilities of these properties (Expt. 1a).
We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
In particular, we hypothesize that different kind--property relations [e.g., *principled* v. *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the feature-probability prior. 
If, in fact, the feature-probability prior is a manifestation of deeper, conceptual knowledge, we would expect the feature-probability prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property.
A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
As a simple test of this hypothesis---that the feature-probability prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

After having validated a measure of the feature-probability prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt. 1b).
In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model. 
To preview our results, we find that only our formulation of an uncertain threshold RSA model is able to account for the flexibility in generic endorsement.

@@

## Experiment 1a: Measuring the feature-probability prior for categories

The feature-probability prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). Ask yourself "is it female?" Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). Now, do you think it lays eggs? Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. That is, the answer is either 50\% or 0\% depending on the kind of creature you are thinking of^[
The subjective probability may, in fact, be non-zero and small for what we're calling 0\%. 
Non-zero probabilities allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with a strange environment. 
].
